Privacy-Respecting Type Error Telemetry at Scale

### 2023-12-08 programming23/artifact/main.tex
artifact more more more

@@

Lines 1-2 of \texttt{out/overview.txt} give the reason for sending:

@@

From \texttt{out/summary-of-size-distributions.rktd}:

@@

\begin{minipage}{0.5\columnwidth}
  \textbf{Timespan:}
  \includegraphics[width=0.4\columnwidth]{out/timespan-distribution.pdf}
\end{minipage}\begin{minipage}{0.5\columnwidth}
  \textbf{Event Count / Record Count:}
  \includegraphics[width=0.4\columnwidth]{out/event-count-distribution.pdf}
\end{minipage}

@@

Correct up/down-grade numbers are in \texttt{out/downgrade-count.txt}:

\includeverbatim{out/downgrade-count.txt}

TODO ^^^

@@

@@

@@

@@

@@

\includegraphics[width=\columnwidth]{out/error-count-nocheck-row--te-density-diff.pdf}
\includegraphics[width=\columnwidth]{out/error-count-nonstrict-row--te-density-diff.pdf}
\includegraphics[width=\columnwidth]{out/error-count-strict-row--te-density-diff.pdf}

>>>>

Plot from \texttt{code/row-distribution.rkt}, which uses the dataset
\texttt{out/row-distribution.rktd}, which comes from running
\texttt{prepare.rkt --mode main}.

@@

Lines 1-2 of \texttt{out/overview.txt} (output of \texttt{prepare.rkt --mode main})
give the reason for sending:

@@

From \texttt{out/summary-of-size-distributions.rktd},\\
which is the output of \texttt{code/sdupdate.rkt}\\
on \texttt{out/size-distributions.rktd}:

@@

\begin{minipage}{0.5\columnwidth}
  \textbf{Timespan:}\\
  \includegraphics[width=0.4\columnwidth]{out/timespan-distribution.pdf}
\end{minipage}\begin{minipage}{0.5\columnwidth}
  \textbf{Event Count / Record Count:}\\
  \includegraphics[width=0.4\columnwidth]{out/event-count-distribution.pdf}
\end{minipage}

@@

Correct up/down-grade numbers are in \texttt{out/downgrade-count.txt},
which is the output of \texttt{code/downgrade-count.rkt} after running
the following commands to generate data:

\begin{verbatim}
PLTSTDERR="error info@luau" racket prepare.rkt --mode divide-sessions
PLTSTDERR="error info@luau" racket prepare.rkt --mode session-query
PLTSTDERR="error info@luau" racket prepare.rkt --mode aggregate-te
\end{verbatim}

% \includeverbatim{out/downgrade-count.txt}

% TODO

@@

These plots come from \texttt{code/error-by-mode.rkt}, which uses
hard-coded data from \texttt{out/overview.txt}:

@@

Output from \texttt{code/type-error-survival.rkt}
run on \texttt{code/type-error-survival-ss-*.rktd}:

@@

Output from \texttt{code/type-error-count.rkt}
run on \texttt{code/te-editrange-ss-*.rktd}:

@@

\subsubsection*{Internal Limits, Code Too Complex}

Data from \texttt{out/ctc-info.txt}, which comes from
\texttt{prepare.rkt --mode main}:

@@

Plot output from \texttt{code/error-count.rkt}
on \texttt{out/error-density-ss-*.rktd}.
(It also prints text output.):

\includegraphics[width=0.8\columnwidth]{out/error-count-nocheck-row--te-density-diff.pdf}
\includegraphics[width=0.8\columnwidth]{out/error-count-nonstrict-row--te-density-diff.pdf}
\includegraphics[width=0.8\columnwidth]{out/error-count-strict-row--te-density-diff.pdf}

\subsection*{Figure 7: Type Error Density}

Shuffled text output from \texttt{code/error-count.rkt}
on \texttt{out/error-density-ss-*.rktd}:

\begin{verbatim}
TE
  nocheck & 48378 & (\pct{46.83}) & 9440 & [\pct{9.14}] & 45479 & [\pct{44.03}] \\
FS
  nocheck & 270763 & (\pct{36.99}) & 238696 & [\pct{32.61}] & 222588 & [\pct{30.41}] \\
TE mod
  nocheck & 20085 & (\pct{49.83}) & 906 & [\pct{2.25}] & 19317 & [\pct{47.92}] \\
FS mod
  nocheck & 259865 & (\pct{39.09}) & 175643 & [\pct{26.42}] & 229271 & [\pct{34.49}] \\
TE
  nonstrict & 19491 & (\pct{39.63}) & 9567 & [\pct{19.45}] & 20121 & [\pct{40.91}] \\
FS
  nonstrict & 35330 & (\pct{37.28}) & 29483 & [\pct{31.11}] & 29955 & [\pct{31.61}] \\
TE mod
  nonstrict & 13030 & (\pct{40.22}) & 5513 & [\pct{17.02}] & 13852 & [\pct{42.76}] \\
FS mod
  nonstrict & 33988 & (\pct{39.74}) & 20738 & [\pct{24.25}] & 30798 & [\pct{36.01}] \\
TE
  strict & 733 & (\pct{39.18}) & 368 & [\pct{19.67}] & 770 & [\pct{41.15}] \\
FS
  strict & 574 & (\pct{33.71}) & 561 & [\pct{32.94}] & 568 & [\pct{33.35}] \\
TE mod
  strict & 419 & (\pct{39.31}) & 230 & [\pct{21.58}] & 417 & [\pct{39.12}] \\
FS mod
  strict & 488 & (\pct{36.53}) & 344 & [\pct{25.75}] & 504 & [\pct{37.72}] \\
\end{verbatim}

### 2023-12-08 programming23/paper.tex
artifact more more more

\begin{table}[t]\centering
  \caption{Current type errors and \FS{} errors across all telemetry records.}
  \label{t:count-analysis-errors}
  \begin{tabular}[t]{ll}
    \begin{tabular}[t]{r@{~~}r@{~}r}
      595,137 & type errors \\
      289,698 & \hbox{}~in module & [\pct{48.68}] \\
       30,924 & \hbox{}~in edit range & [\pct{5.20}]
    \end{tabular}
    \begin{tabular}[t]{r@{~}r@{~}r}
      72,235,735 & {\FS{} errors} \\
      37,027,281 & \hbox{}~in module & [\pct{51.26}] \\
       1,111,178 & \hbox{}~in edit range & [\pct{1.54}]
    \end{tabular}
  \end{tabular}
\end{table}

>>>>

\begin{table}[t]\centering
  \caption{Current type errors and \FS{} errors across all telemetry records.}
  \label{t:count-analysis-errors}
  \begin{tabular}[t]{ll}
    \begin{tabular}[t]{r@{~~}r@{~}r}
      595,137 & type errors \\
      289,698 & \hbox{}~in module & [\pct{48.68}] \\
       30,924 & \hbox{}~in edit range & [\pct{5.20}]
    \end{tabular}
    \begin{tabular}[t]{r@{~~}r@{~}r}
      72,235,735 & {\FS{} errors} \\
      37,027,281 & \hbox{}~in module & [\pct{51.26}] \\
       1,111,178 & \hbox{}~in edit range & [\pct{1.54}]
    \end{tabular}
  \end{tabular}
\end{table}
